---
output:
   bookdown::word_document2:
    number_sections: no
    reference_docx: ./lib/ReportTemplateCalibri.docx
    fig_caption: true
    
params: 
  company: "Janssen Research & Development" 
  reportName: "JNJ-75201646 Whole Blood EC Estimate Analysis"
  identifier: "JNJ-75201646 Whole Blood Cytotoxicity and T Cell Activation Drug Discovery Analysis Report"
  protocol: NULL
  details: "Heme Cancer, Large Molecule, NME Declaration Support"
  primaryCompoundID: "JNJ-75201646"
  reportDate: "November 27, 2020"
  author: "Author's Name (namesurname@its.jnj.com)"
  recipient: "Scientist's Name"
  reportNo: "2021-xxxx"   
  
  endCode: FALSE    #TRUE/FALSE. TRUE: code will be printed at the end of the report, FALSE: only file location is printed at the end of the report
  RmdLocation: "/filepath/HTML Template_Onco"
---


```{r delaycodeprinting, echo = FALSE, message = FALSE, warning = FALSE}
library(knitr)
# The **delaycodeprinting** chunk below allows all R code to be printed at the end of the report (endCode = TRUE) 
#    or prints the RMDLocation from the YAML header as a code reference (endCode != TRUE)
#    see code chunk named 'codeprint'
delay_code_labels <- NULL
knit_hooks$set(delay = function(before, options, envir) {
    if (before) {
        delay_code_labels <<- append(delay_code_labels, options$label)
        return(NULL)  ## otherwise knitr will print delay_code_labels every time
    } else {}
})

if(params$endCode == TRUE){
  opts_chunk$set(delay = TRUE, #Do not change delay = TRUE
                 #You may change global options below
                 echo = FALSE, message = FALSE, warning = FALSE)
} else {
  #You may change global options below
  opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, fig.height  = 4.25)
}
#Read more about R code chunk options: https://yihui.name/knitr/options/#chunk_options
```

<!--- R system setup --->
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r libraries, message = FALSE, warning = FALSE}
#use this block to set libraries, etc
#devtools::install_github("rstudio/rmarkdown")
library(kableExtra)
library(tidyverse)
library(pander)

## SETUP LOCATION
#setwd("/mnt/exports/shared/home/dputri/2019/2019-0542_Scoring system of neurotoxicology study/")

```

<!-------------------------- DO NOT MODIFY TEXT BELOW -------------------------------------> 
<!------------- The following ~30 lines are the first page of the report     --------------> 
<!------------- Any parameter modification should be down in the YAML header --------------> 
<!------------- You can add or delete  to fix title page spacing     --------------> 

<!-------------------------- DO NOT MODIFY TEXT BELOW -------------------------------------> 
<!------------- The following ~30 lines are the first page of the report ------------------> 
<!------------- Any parameter modification should be down in the YAML header --------------> 

\newline

\newline

##### **`r params$company`**

\newline

##### **`r params$reportName`**



***
##### **`r params$identifier`**

***

##### `r params$protocol`  

\newline

##### `r params$details`

\newline

##### `r params$primaryCompoundID`

\newline

\newline

\newline

\newline

\newline

\newline

\newline

\newline

\newline

\newline

\newline

\newline


**Report Date: **	`r params$reportDate`

**Prepared by: **`r params$author`

**Scientific Recipient: **`r params$recipient`

**Report Number: ** `r params$reportNo`

######

<!------------- DO NOT MODIFY TEXT ABOVE THIS COMMENT ------------------> 


<!------------- DO NOT MODIFY FOLLOWING HEADINGS ------------------> 
<!------------- Enter text and code below       -------------------> 

# EXECUTIVE SUMMARY 
\newline

This report is the base for TMEDS group report template in **RMarkdown
Word**. 

[table of contents]

######

# 1. INTRODUCTION 

This report template uses the Iris flower data set as the basis of an example of
an analysis reporting using the TMEDS report template. Additional Rmarkdown
help can be found at this
website: https://github.com/adam-p/markdown-here/wiki/Markdown-Cheatsheet

## 1.1 Background 

\newline

## 1.2 Objectives 

Purpose: to clearly identify key research questions to be investigated.

# 2. METHODOLOGY 

Purpose: to identify and describe the basic elements of statistical analysis,
such as the different models and analysis methods to be used, the underlying
assumptions, decision rules, if any. 


## 2.1 Data Exploration

To be updated

## 2.2 Methods

All analyses were performed in R version `r paste0(version$major,".", version$minor)`.

######

# 3. RESULTS 

This section presents, in a summarized form, the final results from the study.
If the project has undergone numerous revisions in assumptions, scenarios and
focus, then only the more salient results are to be considered. Graphics and
tables should be used to summarize the key results. 


```{r fig1, warning = FALSE, fig.cap = "Scatterplot Matrix of Iris Measures"}
data(iris)

plot(iris$Petal.Length, iris$Petal.Width, pch=21, bg=c("red","green3","blue")[unclass(iris$Species)], 
     main="Edgar Anderson's Iris Data", xlab = "Petal Length", ylab = "Petal Width")
```

Figure \@ref(fig:fig1) shows simple scatter plot of petal length and petal width
from Iris dataset available in R.  

## 3.1 Exploratory data analysis 


 Table \@ref(tab:tab1) presents summary statistics of physical characteristics
of irises by species.  These data are plotted against each other in scatterplots
in Figure \@ref(fig:fig1).

```{r tab1, results = 'asis'}
wdat <-  iris %>% 
		group_by(Species) %>% 
		summarise(meanWidth = mean(Sepal.Width), meanLength = mean(Sepal.Length))

kable(wdat, format = "pipe", caption = "Summary Statistics of Iris Measures by Species")
```

######

## 3.2 Modeling

### 3.2.1 Subsubsection

######


# 4. CONCLUSIONS AND RECOMMENDATIONS

######


# APPENDIX 1: SUPPORTING ANALYSES 


\newline

######

# APPENDIX 2: LIST OF DATASETS AND LOCATION 

\newline

Flow Cytometry data: Whole Blood Spike-in Individual-122319-KP edits.pzfx

Location: jsendeck/Projects/2020/Pillarisetti/2020-12337/dat/

######


# APPENDIX 3: PROGRAMMING CODE  

\newline

```{r codelocation, echo=FALSE, results='asis'}
if(params$endCode != "TRUE"){
  cat(paste("See", params$RmdLocation, "for code details."))
  }

if(params$endCode == "TRUE"){ 
  cat("# Code")
  }  
```

```{r codeprint, echo = TRUE, eval = FALSE, ref.label = delay_code_labels, delay = FALSE}
```

\newline

# R Session Information  

```{r}
pander(sessionInfo(), compact = TRUE)
```

