---
output:
  bookdown::html_document2: 
    number_sections: yes
    fig_caption: true
    toc: yes
    toc_float: yes 
    code_folding: hide
    css: ./lib/stylesArial.css
    anchor_sections: FALSE
    
params: 
  company: "Janssen Research & Development" 
  reportName: "2021-xxxx Drug Discovery Analysis Report"
  identifier: "Project name"
  protocol: NULL
  details: "Heme Cancer, Large Molecule, NME Declaration Support"
  primaryCompoundID: "JNJ-678910, generic name Irisumab"
  reportDate: "format(Sys.time(), '%d %B %Y')"
  author: "Author's Name (namesurname@its.jnj.com)"
  recipient: "Scientist's Name (namesurname@its.jnj.com)"
  reportNo: "2021-xxxx"   
  
  abbreviations: ./dat/Abbreviations.csv
  endCode: FALSE    #TRUE/FALSE. TRUE: code will be printed at the end of the report, FALSE: only file location is printed at the end of the report
  RmdLocation: "/filepath/HTML Template_Onco"
---

```{r logo, echo=FALSE}
# Add logo to the header
htmltools::img(src = knitr::image_uri(file.path("jsn_logo_color_rgb.png")), 
               alt = 'logo', 
               style = 'position: absolute; top:0; right:-5px; padding:10px; height: 125px; width: 210px')
```


```{r delaycodeprinting, echo = FALSE, message = FALSE, warning = FALSE}
library(knitr)
# The **delaycodeprinting** chunk below allows all R code to be printed at the end of the report (endCode = TRUE) 
#    or prints the RMDLocation from the YAML header as a code reference (endCode != TRUE)
#    see code chunk named 'codeprint'
delay_code_labels <- NULL
knit_hooks$set(delay = function(before, options, envir) {
    if (before) {
        delay_code_labels <<- append(delay_code_labels, options$label)
        return(NULL)  ## otherwise knitr will print delay_code_labels every time
    } else {}
})

if(params$endCode == TRUE){
  opts_chunk$set(delay = TRUE, #Do not change delay = TRUE
                 #You may change global options below
                 echo = FALSE, message = FALSE, warning = FALSE)
} else {
  #You may change global options below
  opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
}
#Read more about R code chunk options: https://yihui.name/knitr/options/#chunk_options
```

<!--- R system setup --->
```{r setup, message = FALSE, warning = FALSE}
#use this block to set libraries, etc
#devtools::install_github("rstudio/rmarkdown")
library(kableExtra)
library(tidyverse)
library(pander)

## SETUP LOCATION
#setwd("/mnt/exports/shared/home/dputri/2019/2019-0542_Scoring system of neurotoxicology study/")

```



<!-------------------------- DO NOT MODIFY TEXT BELOW -------------------------------------> 
<!------------- The following ~30 lines are the first page of the report     --------------> 
<!------------- Any parameter modification should be down in the YAML header --------------> 
<!------------- You can add or delete  to fix title page spacing     --------------> 

<!-------------------------- DO NOT MODIFY TEXT BELOW -------------------------------------> 
<!------------- The following ~30 lines are the first page of the report ------------------> 
<!------------- Any parameter modification should be down in the YAML header --------------> 

<br> 
<br> 

<p id="head2"> `r params$company` </p>

<p id="head2"> `r params$reportName` </p>

***
<p id="head2"> `r params$identifier` </p>

***

<p id="head2"> `r params$protocol` </p>

<p id="c11pt"> `r params$details`</p>

<p id="c11pt">`r params$primaryCompoundID`</p>


<p>**Report Date:** `r eval(parse(text = params$reportDate))`</p>

<p>**Prepared by:** `r params$author`</p>

<p>**Scientific Recipient:** `r params$recipient`</p>

<p>**Report Number:** `r params$reportNo`</p>

***

<p id="confhead">Confidentiality Statement</p>

<p id="confbody">The information in this document contains trade secrets and commercial information that are privileged or confidential and may not be disclosed unless such disclosure is required by applicable law or regulations. In any event, persons to whom the information is disclosed must be informed that the information is privileged or confidential and may not be further disclosed by them. These restrictions on disclosure will apply equally to all future information supplied to you that is indicated as privileged or confidential.
</p>

<!------------- DO NOT MODIFY TEXT ABOVE THIS COMMENT ------------------> 


<!------------- DO NOT MODIFY FOLLOWING HEADINGS ------------------> 
<!------------- Enter text and code below       -------------------> 

<p id="head1"> EXECUTIVE SUMMARY </p>

This report is the base for TMEDS group report template in
**RMarkdown HTML**. 






# INTRODUCTION 

This report template uses the Iris flower data set as the basis
of an example of an analysis reporting using the TMEDS report template.
Additional Rmarkdown help can be found at [this
website](https://github.com/adam-p/markdown-here/wiki/Markdown-Cheatsheet).


## Background 


## Objectives 

Purpose: to clearly identify key research questions to be
investigated.






# METHODOLOGY 

Purpose: to identify and describe the basic elements of
statistical analysis, such as the different models and analysis methods to be
used, the underlying assumptions, decision rules, if any. 





## Data Exploration

To be updated



### Subsubsection 

To be updated

## Methods

All analyses were performed in R version `r paste0(version$major,".", version$minor)`.



# RESULTS 

This section presents, in a summarized form, the final results from
the study. If the project has undergone numerous revisions in assumptions,
scenarios and focus, then only the more salient results are to be considered.
Graphics and tables should be used to summarize the key results. 

```{r fig1, warning = FALSE, echo = TRUE, fig.cap = "Scatterplot Matrix of Iris Measures"}
data(iris)

plot(iris$Petal.Length, iris$Petal.Width, pch=21, bg=c("red","green3","blue")[unclass(iris$Species)], 
     main="Edgar Anderson's Iris Data", xlab = "Petal Length", ylab = "Petal Width")
```

Figure \@ref(fig:fig1) shows simple scatter plot of petal length and petal
width from Iris dataset available in R. You can also turn off the code from
printing by changing the parameter `echo = FALSE`. By default, the echo is
always FALSE. 





## Exploratory data analysis 

 Table \@ref(tab:tab1) presents summary statistics of physical
characteristics of irises by species.  These data are plotted against each other
in scatterplots in Figure \@ref(fig:fig1).

```{r tab1, results = 'asis'}
wdat <-  iris %>% 
		group_by(Species) %>% 
		summarise(meanWidth = mean(Sepal.Width), meanLength = mean(Sepal.Length))


kable(wdat, caption = "Summary Statistics of Iris Measures by Species")%>%
  kable_styling(bootstrap_options = c("striped", "condensed"))
```

## Modeling

### Subsubsection






# CONCLUSIONS AND RECOMMENDATIONS

# APPENDIX 1: SUPPORTING ANALYSES 

# APPENDIX 2: LIST OF DATASETS AND LOCATION 

\newline

Flow Cytometry data: Whole Blood Spike-in Individual-122319-KP edits.pzfx

Location: jsendeck/Projects/2020/Pillarisetti/2020-12337/dat/


# APPENDIX 3: PROGRAMMING CODE  

```{r codelocation, echo=FALSE, results='asis'}
if(params$endCode != "TRUE"){
  cat(paste("See", params$RmdLocation, "for code details."))
  }

if(params$endCode == "TRUE"){ 
  cat("# Code")
  }  
```

```{r codeprint, echo = TRUE, eval = FALSE, ref.label = delay_code_labels, delay = FALSE}
```

<p id="head1">R Session Information </p> 

```{r}
pander(sessionInfo(), compact = TRUE)
```

